---
title: "results for PJ 190909"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r 1}
# setup your own paths....
###### REQUIRED LIBRARIES
library(ggplot2)
library(readr)
library(readxl)
library(data.table)
library(rowr)
library(reticulate)
library(scatterplot3d)
library(rgl) #interactive 3d plotting
library(colorspace)
library(ggmin)
library(grid)
library(gridExtra)
library(future)
library(sjmisc)

library(velocyto.R)
library(SeuratWrappers)
library(Seurat)
library(tidyverse)
library(dplyr)

getwd()
```

```{r 2 part1}
getwd()
library(velocyto.R)
library(SeuratWrappers)


```{r 2 part3}
# LOAD
getwd()
setwd("/Users/davidtraver/sc_data_2020")
sampleID <- paste0("14_drl_22hpf.etv2_wt_22hpf.etv2_mib_22hpf.fli1tp1_24hpf","_endo")
name <- paste0(sampleID, ".rds")
UNI <- readRDS(paste0("integratedObjects/",name))
UNI
# genes
markerGenes <- data.frame(read_excel(file.path("Support/scSupport.xlsx"), sheet = "markerGenes", col_names=F, skip=0)) #load our table with markers
#markerGenes <- data.frame(read_excel(file.path("../Support/scSupport.xlsx"), sheet = "markerGenesTimepoint", col_names=F, skip=0))
str(markerGenes)
  # Particular column select
{  markerx <- as.vector(markerGenes[1:nrow(markerGenes),c(9,20)]) #column no. or markerGenes$HSC, was notch, but changed to HSCs
  markerx <- markerx[!is.na(markerx)]
  markert <- as.vector(markerx[1])
  markerx <- as.vector(markerx[2:length(markerx)])
}
    markert
    markerx
    
      markerx_UNI <- character()
      markerx_UNI <- sapply(markerx, function(x) {sort(grep(pattern = paste0("^",x), rownames(UNI[["SCT"]]@data), value= T, ignore.case = T))})
      markerx_UNI <- unlist(markerx_UNI)
      markerx_UNI <- sort(unique(as.vector(markerx_UNI)))
        markerx_UNI

# idents
  Idents(object = UNI) <- "customNames"
  table(Idents(UNI))

dim1 <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim1

  Idents(object = UNI) <- "OLDsampleID"
  table(Idents(UNI))

dim2 <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim2  
  
UNI <- subset(UNI, cells = WhichCells(UNI, ident = (c("etv2_wt_22hpf", "etv2_mib_22hpf"))), max.cells.per.ident = Inf, random.seed = 1)
dim3 <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim3

#HM all endo
All.markers <- FindAllMarkers(object = UNI, only.pos = T, min.pct = 0.25, logfc.threshold = 0.20, return.thresh = 0.1) #return.tresh to find the same as FindMarkers
head(All.markers)
write.csv(All.markers, "./export/190909/2/2_part3_DE_endothelium_22hpf_WTxMIB.csv")
topAll <- All.markers %>% group_by(cluster) %>% arrange(desc(avg_logFC)) %>% top_n(20, avg_logFC) %>% filter(avg_logFC>0.1)
topAll

#levels(UNI)
#levels(UNI) <- c("General Endothelium","Hemogenic endothelium","Pre-HCSs","BVECs","Endocardium","KVECs","SDECs")
all <- DoHeatmap(UNI, features = topAll$gene, cells = WhichCells(UNI, idents = NULL, downsample = 250), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim4a <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="all endothelium_DE")
dim4a


#HM all endo 0 ribo
ribo <- !grepl("^rp|^RPS|^RPL|^mt-", All.markers$gene)
ribo
All.markers0ribo <- All.markers[ribo,]
topAll <- All.markers0ribo %>% group_by(cluster) %>% arrange(desc(avg_logFC)) %>% top_n(20, avg_logFC) %>% filter(avg_logFC>0.1)
topAll

all <- DoHeatmap(UNI, features = topAll$gene, cells = WhichCells(UNI, idents = NULL, downsample = 250), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim4b <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="all endothelium_DE no ribo")
dim4b



#HM for SDEC genes
SDECgenes <- c("bmp4", "cxcr4a", "cxcr4b", "cldni", "tmsb1", "col7a1", "tp63", "lama5", "mmp30", "sparc", "dcn", "apoeb", "angptl4")  
SDECgenes
All.markers <- FindAllMarkers(object = UNI, features = SDECgenes, only.pos = T, min.pct = 0.0001, logfc.threshold = 0.00001, return.thresh = 1000) #return.tresh to find the same as FindMarkers
topAll <- All.markers %>% group_by(cluster) %>% arrange(desc(avg_logFC)) %>% top_n(20, avg_logFC) %>% filter(avg_logFC>0.00001)
topAll

write.csv(All.markers, "./export/190909/2/2_part3_DE_endothelium-SDECgenes_22hpf_WTxMIB.csv")

all <- DoHeatmap(UNI, features = topAll$gene, cells = WhichCells(UNI, idents = NULL, downsample = Inf), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim4c <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="mib vs wt SDEC genes")
dim4c


#HM notch
all <- DoHeatmap(UNI, features = markerx_UNI, cells = WhichCells(UNI, idents = NULL, downsample = 250), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim5 <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="all endothelium_notch related")
dim5

  Idents(object = UNI) <- "customNames"
  table(Idents(UNI))
  
UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Pre-HCSs", "Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
dim6 <- DimPlot(UNIp, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim6
FeaturePlot(UNIp, order = T, features = c("gfi1aa","myb", "cebpa"), pt.size=3, split.by = "OLDsampleID")
  
  table(Idents(UNIp))
  Idents(object = UNIp) <- "OLDsampleID"
  table(Idents(UNIp))


all <- DoHeatmap(UNIp, features = markerx_UNI, cells = WhichCells(UNIp, idents = NULL, downsample = 50), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim7 <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="Pre-HCS and Hemogenic endothelium_notch related")
dim7

markerx_UNI[c(1,3,8,9)]

#C1.markers <- FindMarkers(object = UNI, ident.1 = c("etv2_wt_22hpf"), ident.2 = c("etv2_mib_22hpf"), logfc.threshold = 0.20, min.pct = 0.25)
#C1.markers <- cbind(gene = rownames(C1.markers), C1.markers)
#head(C1.markers)
#topC1a <- C1.markers %>% top_n(20, desc(avg_logFC)) %>% arrange(avg_logFC) %>% filter(avg_logFC < 0)
#topC1b <- C1.markers %>% top_n(20, avg_logFC) %>% arrange(desc(avg_logFC)) %>% filter(avg_logFC > 0)
#topC1 <- union(topC1a, topC1b)  %>% arrange(avg_logFC)
#topC1
#
#all <- DoHeatmap(UNI, features = union(topC1a$gene, topC1b$gene), cells = WhichCells(UNI, idents = NULL, downsample = 25), group.by = "ident", group.bar = T, #disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = #TRUE, group.bar.height = 0.000000001)
#dim5 <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE)
#


getwd()
pdf(paste0("./export/190909/2/", "2_part3v2.pdf"), width=15,height=10)
dim1
dim2
dim3
dim4a
dim4b
dim5
for (i in 1:ceiling(length(markerx_UNI))) {
 tmp <- markerx_UNI[i]
 plot <-     FeaturePlot(UNI, order = T, features = tmp, cols =c("light grey", "dark red"), min.cutoff= NA, max.cutoff= NA, reduction = "umap", dims = c(1,2), pt.size=2, ncol=2, split.by = "OLDsampleID")
print(plot) + labs(title="all endothelium_notch related")}

dim6
dim7
for (i in 1:ceiling(length(markerx_UNI))) {
 tmp <- markerx_UNI[i]
 plot <-     FeaturePlot(UNI, order = T, features = tmp, cols =c("light grey", "dark red"), min.cutoff= NA, max.cutoff= NA, reduction = "umap", dims = c(1,2), pt.size=2, ncol=2, split.by = "OLDsampleID")
print(plot) + labs(title="Pre-HCS and Hemogenic endothelium_notch related")}
dev.off()
```

```{r 3}
{                           no <- 5