---
title: "results for PJ 190909"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r 1}
# setup your own paths....
###### REQUIRED LIBRARIES
library(ggplot2)
library(readr)
library(readxl)
library(data.table)
library(rowr)
library(reticulate)
library(scatterplot3d)
library(rgl) #interactive 3d plotting
library(colorspace)
library(ggmin)
library(grid)
library(gridExtra)
library(future)
library(sjmisc)

library(velocyto.R)
library(SeuratWrappers)
library(Seurat)
library(tidyverse)
library(dplyr)

setwd("/Users/davidtraver/sc_data_2020")
getwd()

sampleID <- paste0("14_drl_22hpf.etv2_wt_22hpf.etv2_mib_22hpf.fli1tp1_24hpf","_endo")

name <- paste0(sampleID, ".rds")
UNI <- readRDS(paste0("./integratedObjects/",name))
# idents
  Idents(object = UNI) <- "customNames"
  table(Idents(UNI))

dim1 <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim1
  Idents(object = UNI) <- "OLDsampleID"
  table(Idents(UNI))
dim2 <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title=sampleID)
dim2 

UNI <- subset(UNI, cells = WhichCells(UNI, ident = (c("etv2_wt_22hpf", "etv2_mib_22hpf"))), max.cells.per.ident = Inf, random.seed = 1)
dim3a <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1) + labs(title="etv2_wt_22hpf + etv2_mib_22hpf")
dim3a
  Idents(object = UNI) <- "customNames"
  table(Idents(UNI))

dim3b <- DimPlot(UNI, label=T, label.size = 8, pt.size = 1, split.by = "OLDsampleID") + labs(title=NULL)
dim3b

#HM for SDEC genes####
SDECgenes <- c("cldni", "tmsb1", "col7a1", "tp63", "lama5", "mmp30", "sparc", "dcn", "apoeb", "angptl4", "bmp4") 
SDECgenes

All.markers <- FindAllMarkers(object = UNI, features = SDECgenes, only.pos = T, min.pct = 0.0001, logfc.threshold = 0.00001, return.thresh = 1000) #return.tresh to find the same as FindMarkers
topAll1 <- All.markers %>% group_by(cluster) %>% arrange(desc(avg_logFC)) %>% top_n(20, avg_logFC) %>% filter(avg_logFC>0.00001)
topAll1

  Idents(object = UNI) <- "OLDsampleID"
all <- DoHeatmap(UNI, features = topAll1$gene, cells = WhichCells(UNI, idents = NULL, downsample = 250), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)

dim4a <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="mib vs wt (all endo) SDEC genes")
dim4a

Idents(UNI) <- "OLDsampleID"
avg.UNI <- log1p(AverageExpression(UNI, verbose = T, assays = "SCT")$SCT)
avg.UNI$gene <- rownames(avg.UNI)
X <- colnames(avg.UNI[1])
Y <- colnames(avg.UNI[2])
colnames(avg.UNI) <- c("x", "y","gene")
head(avg.UNI)
```


```{r 1}
genes.to.label <- topAll1$gene
p1 <- ggplot(avg.UNI, aes(x,y)) + geom_point() + ggtitle(sampleID) + labs(title = sampleID, x = X, y = Y)
dim4b <- LabelPoints(plot = p1, points = genes.to.label, repel = T, ynudge = 0.1) + labs(title="mib vs wt (all endo) SDEC genes")
dim4b
```


```{r 1}
Idents(object = UNI) <- "customNames"

UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("SDECs"))), max.cells.per.ident = Inf, random.seed = 1)
#UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Pre-HCSs", "Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
#UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
dim4c <- DimPlot(UNIp, label=T, label.size = 8, pt.size = 1) + labs(title="mib vs wt (SDECs)")
dim4c

  Idents(object = UNIp) <- "OLDsampleID"

all <- DoHeatmap(UNIp, features = topAll1$gene, cells = WhichCells(UNIp, idents = NULL, downsample = 100), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)

dim4d <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="mib vs wt (SDECs) SDEC genes")

dim4d
###########################################################################################################
Idents(UNIp) <- "OLDsampleID"
UNIt <- subset(UNIp, cells = WhichCells(UNI, ident = (c("etv2_wt_22hpf", "etv2_mib_22hpf"))), max.cells.per.ident = Inf, random.seed = 1)

Idents(UNIp) <- "OLDsampleID"
Idents(UNIp) <- "OLDsampleID"
str(UNIp)
head(UNIp)
avg.UNI <- log1p(AverageExpression(UNIp, verbose = T, assays = "SCT")$SCT)
avg.UNI$gene <- rownames(avg.UNI)
head(avg.UNI$gene, 10)
X <- colnames(avg.UNI[1])
Y <- colnames(avg.UNI[2])
colnames(avg.UNI) <- c("x", "y","gene")

head(avg.UNI[1], 20)
tail(avg.UNI, 20)

genes.to.label <- c('ptpn12', 'dusp16', 'crebl2', 'tbk1', 'msgn1', 'CU856344.1', "si:ch211-51e12.7")

genes.to.label <- c('id1', 'glula', 'hmgn2', 'gpr182', 'egf17', 'cdh5', 'rab11b', 'tpm4a', 'tie1', 'clec14a', 'pmp22a', 'tmsb4x', 'krt4', 'pleca','cyt1', 'tmsb1', 'faua', 'egfl7', )

genes.to.label <- c('id1', 'glula', 'hmgn2', 'gpr182', 'egf17', 'cdh5', 'rab11b', 'tpm4a', 'tie1', 'clec14a', 'pmp22a', 'tmsb4x', 'krt4', 'pleca','cyt1', 'tmsb1', 'faua', 'egfl7', 'efnb2a', 'dll4', 'hey2', 'notch')

genes.to.label <- topAll1$gene

p1 <- ggplot(avg.UNI, aes(x,y)) + geom_point() + ggtitle(sampleID) + labs(title = sampleID, x = X, y = Y)
dim4e <- LabelPoints(plot = p1, points = genes.to.label, repel = T, color='red', ynudge = 0.1) + labs(title="mib vs wt (SDECs) SDEC genes")
dim4e


#HM notch####

# genes
markerGenes <- data.frame(read_excel(file.path("../Support/scSupport.xlsx"), sheet = "markerGenes", col_names=F, skip=0))
str(markerGenes)
  # Particular column select
{  markerx <- as.vector(markerGenes[1:nrow(markerGenes),c(9,20)]) #column no. or markerGenes$HSC, was notch, but changed to HSCs
  markerx <- markerx[!is.na(markerx)]
  markert <- as.vector(markerx[1])
  markerx <- as.vector(markerx[2:length(markerx)])
}
    markert
    markerx
      markerx_UNI <- character()
      markerx_UNI <- sapply(markerx, function(x) {sort(grep(pattern = paste0("^",x), rownames(UNI[["SCT"]]@data), value= T, ignore.case = T))})
      markerx_UNI <- unlist(markerx_UNI)
      markerx_UNI <- sort(unique(as.vector(markerx_UNI)))

        markerx_UNI

All.markers <- FindAllMarkers(object = UNI, features = markerx_UNI, only.pos = T, min.pct = 0.0001, logfc.threshold = 0.00001, return.thresh = 1000) #return.tresh to find the same as FindMarkers
topAll2 <- All.markers %>% group_by(cluster) %>% arrange(desc(avg_logFC)) %>% top_n(20, avg_logFC) %>% filter(avg_logFC>0.00001)
topAll2

  Idents(object = UNI) <- "OLDsampleID"

all <- DoHeatmap(UNI, features = topAll2$gene, cells = WhichCells(UNI, idents = NULL, downsample = 250), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)

dim5a <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="mib vs wt (all endo) HSC genes")
dim5a

##################################### TEST  ########################################
Idents(UNI) <- "OLDsampleID"
avg.UNI <- log1p(AverageExpression(UNI, verbose = T, assays = "SCT")$SCT)
avg.UNI$gene <- rownames(avg.UNI)
X <- colnames(avg.UNI[1])
Y <- colnames(avg.UNI[2])
colnames(avg.UNI) <- c("x", "y","gene")
head(avg.UNI, 30)
tail(avg.UNI, 30)
##################################### TEST  ########################################

genes.to.label <- topAll2$gene
p1 <- ggplot(avg.UNI, aes(x,y)) + geom_point() + ggtitle(sampleID) + labs(title = sampleID, x = X, y = Y)
dim5b <- LabelPoints(plot = p1, points = genes.to.label, repel = T, ynudge = 0.1, colour = "red") + labs(title="mib vs wt (all endo) HSC genes")
dim5b

  Idents(object = UNI) <- "customNames"
#UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("SDECs"))), max.cells.per.ident = Inf, random.seed = 1)
UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Pre-HCSs", "Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
#UNIp <- subset(UNI, cells = WhichCells(UNI, ident = (c("Hemogenic endothelium"))), max.cells.per.ident = Inf, random.seed = 1)
dim5c <- DimPlot(UNIp, label=T, label.size = 8, pt.size = 1) + labs(title="mib vs wt (Pre-HCSs + Hemogenic endothelium)")
dim5c

  Idents(object = UNIp) <- "OLDsampleID"
all <- DoHeatmap(UNIp, features = topAll2$gene, cells = WhichCells(UNIp, idents = NULL, downsample = 100), group.by = "ident", group.bar = T, disp.min = -2, disp.max = NULL, slot = "scale.data", assay = "SCT", label = T, size = 5, hjust = 0.5, angle = 0, draw.lines = T, raster = TRUE, combine = TRUE, group.bar.height = 0.000000001)
dim5d <- all + scale_fill_gradientn(colors = rev(RColorBrewer::brewer.pal(n = 10, name = "RdBu")), na.value = "white") + guides(color=FALSE) + labs(title="mib vs wt (Pre-HCSs + Hemogenic endothelium) HSC genes")
dim5d

Idents(UNIp) <- "OLDsampleID"
avg.UNI <- log1p(AverageExpression(UNIp, verbose = T, assays = "SCT")$SCT)
avg.UNI$gene <- rownames(avg.UNI)
X <- colnames(avg.UNI[1])
Y <- colnames(avg.UNI[2])
colnames(avg.UNI) <- c("x", "y","gene")
head(avg.UNI)

genes.to.label <- topAll2$gene
p1 <- ggplot(avg.UNI, aes(x,y)) + geom_point() + ggtitle(sampleID) + labs(title = sampleID, x = X, y = Y)
dim5e <- LabelPoints(plot = p1, points = genes.to.label, repel = T, ynudge = 0.1, colour = "red") + labs(title="mib vs wt (Pre-HCSs + Hemogenic endothelium) HSC genes")
dim5e

getwd()

pdf(paste0("./export/190909/4/", "200324.pdf"), width=15,height=10)
dim1
dim2
dim3a
dim3b

dim4a
dim4b
dim4c
dim4d
dim4e

for (j in seq(1,length(topAll1$gene),1)) {

plot <- FeaturePlot(UNI, order = T, features = topAll1$gene[j], min.cutoff= NA, max.cutoff= NA, reduction = "umap", dims = c(1,2), pt.size=2, shape.by = "OLDsampleID", blend = F) + facet_wrap("OLDsampleID", ncol=2) + guides(shape = F) + theme(legend.text = element_text(size = 5), legend.key.size = unit(0.5, "inch"), legend.key.width = unit(0.1,"inch") )

print(plot)

}
dim3b

 

dim5a

dim5b

dim5c

dim5d

dim5e

for (j in seq(1,length(topAll2$gene),1)) {

plot <- FeaturePlot(UNI, order = T, features = topAll2$gene[j], min.cutoff= NA, max.cutoff= NA, reduction = "umap", dims = c(1,2), pt.size=2, shape.by = "OLDsampleID", blend = F) + facet_wrap("OLDsampleID", ncol=2) + guides(shape = F) + theme(legend.text = element_text(size = 5), legend.key.size = unit(0.5, "inch"), legend.key.width = unit(0.1,"inch") )

print(plot)

}

dev.off()